Curve counting in genus one: elliptic singularities and relative geometry

### 2019-06-27 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
improvements to 5.3.3

\subsection{Recursive description of the divisors: types $A,B$ and $C^+$} Choose an irreducible component $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$. By Lemma \ref{Lemma components are log divisors} this is a log divisor, and hence may be written as:
\begin{equation*} \Dcal = \widetilde\Dcal \cap \VZ_{1,\alpha}(\PP^N|H,d) \end{equation*}
for a unique log stratum $\widetilde\Dcal \subseteq \widetilde{\VZ}_{1,\alpha}(\PP^N|H,d)$. Since
\begin{equation*}\widetilde{\VZ}_{1,\alpha}(\PP^N|H,d) \to \ol\Mcal_{1,\alpha}(\PP^N|H,d)\end{equation*}
is a log modification, $\widetilde{\Dcal}$ is either exceptional or the proper transform of a log divisor. These cases correspond, respectively, to when the core is assigned zero degree or nonzero degree by the combinatorial type. To begin with we will focus on the latter case. Suppose therefore that $\widetilde{\Dcal}$ is the proper transform of a log divisor:
\begin{equation*} \Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d). \end{equation*}
The birational map $\widetilde{\Dcal} \to \Ecal$ induces a morphism $\Dcal \to \Ecal$. In the remainder of this subsection, we will show how to interpret this morphism as a ``desingularisation of the main component''. Since $\Ecal$ admits a recursive description in terms of relative and rubber moduli spaces, this will allow us to compute integrals over $\Dcal$.

@@

\subsubsection{Possible combinatorial types} Recall that a boundary divisor $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ is said to be of type IIIb if the core is assigned degree zero by the combinatorial type (this is the case which was ignored in Lemma \ref{lem:combs} and the subsequent discussion). In this case, the combinatorial type is not as tightly constrained as before; the target may expand multiple times, and as such the combinatorial type need not be a bipartite graph with a single interior vertex. Nevertheless, we have the following lemma:
\begin{lemma} 
Let $\Dcal$ be a locus of type IIIb and let $\Delta$ be the corresponding combinatorial type. Then for every nonzero vertex $\diamond$ of the expanded tropical target, the fibre of the tropical map over $\diamond$ contains exactly one stable vertex, which lies on the radius.
\end{lemma}
\begin{proof}
By stability, we must always have at least one stable vertex lying over each  vertex of the target. If there was more than one, then (since both the insertions and the factorisation condition are pulled back from the moduli space of maps without expansions) we can show, as in the proof of Lemma \ref{lem:combs}, that the contribution vanishes.

@@

A priori it could be that the stable vertex is not amongst those vertices lying on the radius. But in this case the corresponding locus $\Fcal$ in the moduli space of unexpanded maps has larger codimension (for the same reason as before), and so the contribution vanishes by the projection formula. 
\end{proof}

\subsubsection{Recursive description of $\Ecal$}
Just as before, we let $\tau \in \Sigma$ be the ray corresponding to $\Dcal \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$, $\sigma \in \Sigma^{\Kim}$ be the minimal cone containing $\tau$ and $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ be the stratum corresponding to $\sigma$, so that we have a map $\Dcal \to \Ecal$ (and $\Ecal$ is the minimal stratum through which the map from $\Dcal$ factors). Recall that we also have a unique stratum $\widetilde\Dcal \subseteq \widetilde\VZ_{1,\alpha}(\PP^N|H,d)$ such that $\Dcal = \widetilde\Dcal \cap \VZ_{1,\alpha}(\PP^N|H,d)$. Note that the cone $\sigma$ has dimension equal to the number of levels of the target expansion in the combinatorial type, which in this case could possibly be larger than $1$.

@@

Notice that the actual dimension of $\Ecal$ will typically be larger than that of $\Dcal$, since $\Ecal$ is contained inside the excess components of the moduli space. We will explain how to compute integrals over $\Dcal$ in two steps:
\begin{enumerate}
\item we explain how to construct $\widetilde\Dcal$ from $\Ecal$ in \S \ref{};
\item we explain how to express the class of $\Dcal \subseteq \widetilde\Dcal$ in terms of tautological classes in \S \ref{}.
\end{enumerate}

@@

\subsubsection{$\widetilde\Dcal$ from $\Ecal$} Recall that the map $\widetilde\Dcal \to \Ecal$ is obtained by restricting the logarithmic blow-up
\begin{equation*} \widetilde\VZ_{1,\alpha}(\PP^N|H,d) \to \ol\Mcal_{1,\alpha}(\PP^N|H,d)\end{equation*}
to the locus $\widetilde\Dcal$. In toric geometry, the method for studying this restriction is as follows. The fan of $\widetilde\Dcal$ (respectively, $\Ecal$) is obtained by projecting the star of the ray $\tau$ (respectively, the cone $\sigma$) onto the quotient lattice. The map $\widetilde\Dcal \to \Ecal$ is then a toric morphism, induced by the obvious map of fans. In order to describe this morphism, we first subdivide the fan of $\Ecal$ by taking the images of cones in the fan of $\widetilde\Dcal$. This induces a toric blow-up of $\Ecal$ which we denote by $\widetilde\Ecal$. The morphism $\widetilde\Dcal \to \Ecal$ naturally factors through a morphism $\widetilde\Dcal \to \widetilde\Ecal$ which is now flat (in contrast to $\widetilde\Dcal \to \Ecal$), and now $\Dcal$ can be described as a compactification of a torus bundle over $\widetilde\Ecal$, with strata determined by the combinatorics of the fan.

Returning to the logarithmic setting, the first step is to define appropriate logarithmic structures on $\widetilde\Dcal$ and $\Ecal$. We equip $\widetilde\Dcal$ with the logarithmic structure obtained by first restricting the logarithmic structure on $\widetilde\VZ_{1,\alpha}(\PP^N|H,d)$ and then quotienting by the normal direction to $\widetilde\Dcal$. By the same process we may also define a logarithmic structure on $\Ecal$, and this coincides with the pull-back along $\rho$ of the product logarithmic structure on the fibre product in \eqref{IIIa fibre product}. The map $\widetilde\Dcal \to \Ecal$ is then naturally a logarithmic map.

The next step is to construct $\widetilde\Ecal$ as a logarithmic modification of $\Ecal$, and to do this we need to describe the tropicalisation of the map $\widetilde\Dcal \to \Ecal$. In fact, it is more convenient to consider the \emph{extended tropicalisation} \cite{}. We begin by fixing notation. Associated to the combinatorial type $\Delta$, we have stable vertices $\sqC_0,\sqC_1,\ldots,\sqC_r$ with $\sqC_0$ corresponding to the core and $\sqC_1,\ldots,\sqC_r$ corresponding to stable vertices which lie on the raidus (see Lemma \ref{} above). For $i \in \{1,\ldots,r\}$ let $e_i$ denote the sum of the edge lengths separating $\sqC_i$ from $\sqC_0$. These give functions on the cone $\sigma$, and $\tau$ is the ray given by the equations $e_1=\ldots=e_r$. Note that the $e_i$ also define functions on any cone in the star of $\sigma$.

@@

Consider any cone $\rho$ in the star of $\tau$. Since the tropicalisation of $\widetilde\VZ_{1,\alpha}(\PP^N|H,d)$ is a subdivision of the tropicalisation of $\ol\Mcal_{1,\alpha}(\PP^N|H,d)$ there is a unique minimal cone in the star of $\sigma$ which contains $\rho$. We denote this cone by $\theta$, and remark that $\theta$ arises from a choice of combinatorial type which specialises the combinatorial type $\Delta$ defining $\sigma$. On $\theta$ we have the edge length functions $e_1,\ldots,e_r$ as well as additional edge lengths corresponding to nodes on $\theta$ which are smoothed out on $\sigma$.

Now, $\rho$ is defined inside $\theta$ by a number of equalities and inequalities involving these edge lengths. These (in)equalities relate the distances to the core of various vertices of the dual graph. There are three cases we must consider:
\begin{enumerate}
\item both vertices are components of $\sqC_1 \cup \ldots \cup \sqC_r$;
\item both vertices are components of $\sqC_0$;
\item one vertex is a component of $\sqC_0$ and one is a component of $\sqC_1 \cup \ldots \cup\sqC_r$.
\end{enumerate}
We start with case (1). By the definition of a well-spaced tropical map, we see that these are all of the form
\begin{equation*} f_i + e_i = f_j + e_j \end{equation*}
where $f_i$ and $f_j$ are positive linear combinations of additional edge length parameters which are set to zero in $\tau$. We may now pass to the subcone of $\rho$ obtained by imposing the additional equations $e_1=\ldots=e_r$. Note that this is \emph{not} a subcone of $\tau$ in general, since there are additional edge lengths which must be set to zero if one wishes to recover $\tau$. The additional equations mean that we can rewrite our previous (in)equalities in the form
\begin{equation*} f_i = f_j \end{equation*}
and these define a cone in the limiting locus $e_1=\ldots=e_r=\infty$. By definition this is one of the cones in the subdivision of the extended tropicalisation of $\Ecal$, and all such cones are obtained in this manner.

Taking this subdivision amounts to the following modular blow-up of the fibre product of the moduli spaces attached to the vertices $\sqC_1,\ldots,\sqC_r$: given a logarithmic map with splitting nodes $q_1,\ldots,q_r$ as specified by the shape of $\Delta$, we glue together the $r$ vertices of the tropicalisation which carry the splitting nodes, and declare the resulting special vertex to be the root of the resulting tree. We then impose a central alignment condition, entirely analogous to the genus one construction, where the special root takes on the role previously occupied by the core.

We now deal with Case (2). These (in)equalities are not affected at all in the limit $e_1=\ldots=e_r=\infty$ and so the effect is to replace the factor of $\Ecal$ attached to the vertex $\sqC_0$
\begin{equation*} \ol\Mcal^{\leftrightarrow}_{\Gamma_{\tiny{\sqC_0}}}(P|H_0+H_\infty) \end{equation*}
with the radially aligned rubber space:
\begin{equation*} \VZ^{\leftrightarrow}_{\Gamma_{\tiny{\sqC_0}}}(P|H_0+H_\infty).\end{equation*}
The factorisation condition here is accounting for the ``fibre-direction'' factorisation; the ``base-direction'' factorisation has not entered the picture yet, and will appear when we come to describe $\Dcal$.

It remains to discuss Case (3). Here we have a relation of the form $f_i = f_j + e_j$, so in the limit $e_j =\infty$ there is no limiting cone. Therefore these relations to not appear in the modification of $\Ecal$.

In this way, we obtain a logarithmic modification $\tilde\Ecal \to \Ecal$. By definition the map $\tilde\Dcal \to \Ecal$ is a compactification of a torus bundle over $\Ecal$, whose strata can be read off from the tropicalisation of $\tilde\Dcal$.

@@

\subsubsection{$\Dcal$ from $\widetilde\Dcal$} On $\widetilde\Dcal$ there is a natural vector bundle arising from the modular desription of $\widetilde\VZ_{1,\alpha}(\PP^N|H,d)$, namely:
\begin{equation*} F = \OO(\delta)^{\oplus r}. \end{equation*}
We claim that the fibre of $F$ over a moduli point can be naturally identified with
\begin{equation*} \left( \bigoplus_{i=1}^r \TT_{p_i} C_i^\prime \right) \otimes \TT_{C_0} \end{equation*}
where $C_i^\prime$ is a component of $C_i$ which lies on the radius, $p_i$ is the adjacent node which points towards the core, and $\TT_{C_0}$ is the universal tangent line bundle on the radially aligned rubber space.

>>>>

\subsection{Recursive description of the divisors: types $A,B$ and $C^+$}\label{subsection:ABC description} Choose an irreducible component $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$. By Lemma \ref{Lemma components are log divisors} this is a log divisor, and hence may be written as:
\begin{equation*} \Dcal = \widetilde\Dcal \cap \VZ_{1,\alpha}(\PP^N|H,d) \end{equation*}
for a unique log stratum $\widetilde\Dcal \subseteq \widetilde{\VZ}_{1,\alpha}(\PP^N|H,d)$. Since
\begin{equation*}\widetilde{\VZ}_{1,\alpha}(\PP^N|H,d) \to \ol\Mcal_{1,\alpha}(\PP^N|H,d)\end{equation*}
is a log modification, $\widetilde{\Dcal}$ is either exceptional or the proper transform of a log divisor. These cases correspond, respectively, to when the core is assigned zero degree or nonzero degree by the combinatorial type. To begin with we will focus on the latter case. Suppose therefore that $\widetilde{\Dcal}$ is the proper transform of a log divisor:
\begin{equation*} \Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d). \end{equation*}
The birational map $\widetilde{\Dcal} \to \Ecal$ induces a morphism $\Dcal \to \Ecal$. In the remainder of this subsection, we will show how to interpret this morphism as a ``desingularisation of the main component''. Since $\Ecal$ admits a recursive description in terms of relative and rubber moduli spaces, this will allow us to compute integrals over $\Dcal$.

@@

\subsubsection{Possible combinatorial types} Recall that a boundary divisor $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ is said to be of type IIIb if the core is assigned degree zero by the combinatorial type (this is the case which was ignored in Lemma \ref{lem:combs} and the subsequent discussion). In this case, the combinatorial type is not as tightly constrained as before; the generic target may expand multiple times, and as such the combinatorial type need not be a bipartite graph with a single interior vertex. Nevertheless, we have the following lemma:
\begin{lemma} \label{lemma type C0 combinatorial types}
Let $\Dcal$ be a locus of type IIIb and let $\Delta$ be the corresponding combinatorial type. Then for every nonzero vertex $\diamond$ of the expanded tropical target, the fibre of the tropical map over $\diamond$ contains exactly one stable vertex, which lies on the radius.
\end{lemma}
\begin{proof}
By stability, we must always have at least one stable vertex lying over each  vertex of the target. If there is more than one then, as in the proof of Lemma \ref{lem:combs} above, we see that the corresponding locus $\Fcal$ in the moduli space of unexpanded maps has larger codimension and so (since both the insertions and the factorisation condition are pulled back from the moduli space of maps without expansions) the contribution vanishes by the projection formula.

@@

A priori it could be that the stable vertex is not among those vertices over $\diamond$ which lie on the radius. But in this case we we have a trivial bubble lying on the radius; this implies the map $\Dcal \to \Ecal$ has positive-dimensional fibres, since the derivative of the stable map on the trivial bubble will always be zero (for a more detailed discussion, see \S \ref{} below). Hence, the contribution from these loci vanishes.
\end{proof}

\subsubsection{Recursive description of $\Ecal$}
Just as in \S \ref{subsection:ABC description}, we let $\tau \in \Sigma$ be the ray corresponding to $\Dcal \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$, $\sigma \in \Sigma^{\Kim}$ be the minimal cone containing $\tau$ and $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ be the stratum corresponding to $\sigma$, so that we have a map $\Dcal \to \Ecal$ and $\Ecal$ is the minimal stratum through which the map $\Dcal \to \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ factors. Recall that we also have a unique stratum $\widetilde\Dcal \subseteq \widetilde\VZ_{1,\alpha}(\PP^N|H,d)$ such that $\Dcal = \widetilde\Dcal \cap \VZ_{1,\alpha}(\PP^N|H,d)$. Note that the cone $\sigma$ has dimension equal to the number of levels of the target expansion in the combinatorial type, which in this case could possibly be larger than $1$.

@@

Notice that the actual dimension of $\Ecal$ will typically be larger than that of $\Dcal$, since $\Ecal$ is contained inside the excess components of the moduli space. In the remainder of this section, we will reduce integrals over $\Dcal$ to certain excess integrals over $\Ecal$. We proceed in two steps:
\begin{enumerate}
\item in \S \ref{subsection Dtilde from E} we explain how to construct $\widetilde\Dcal$ from $\Ecal$;
\item in \S \ref{subsection D from Dtilde} we explain how to express the class of $\Dcal \subseteq \widetilde\Dcal$ in terms of tautological classes.
\end{enumerate}
To compute integrals over $\Dcal$ we simply push down the appropriate classes from $\widetilde\Dcal$ to $\Ecal$ and then integrate over $\Ecal$ using the ordinary splitting axiom.

@@

\subsubsection{$\widetilde\Dcal$ from $\Ecal$}\label{subsection Dtilde from E} Recall that the map $\widetilde\Dcal \to \Ecal$ is obtained by restricting the logarithmic blow-up
\begin{equation*} \widetilde\VZ_{1,\alpha}(\PP^N|H,d) \to \ol\Mcal_{1,\alpha}(\PP^N|H,d)\end{equation*}
to the locus $\widetilde\Dcal$. In toric geometry, the means of studying this restriction is as follows. The fan of $\widetilde\Dcal$ (respectively, $\Ecal$) is obtained by projecting the star of the ray $\tau$ (respectively, the star of the cone $\sigma$) onto the quotient lattice. The map $\widetilde\Dcal \to \Ecal$ is then the toric morphism induced by the obvious map of fans. In order to describe this morphism more explicitly, we first subdivide the fan of $\Ecal$ by taking the images of cones in the fan of $\widetilde\Dcal$. This induces a toric blow-up of $\Ecal$ which we denote by $\widetilde\Ecal$. The morphism $\widetilde\Dcal \to \Ecal$ naturally factors through a morphism $\widetilde\Dcal \to \widetilde\Ecal$ which is now flat (in contrast to $\widetilde\Dcal \to \Ecal$), and  $\widetilde\Dcal$ may now be described as a compactification of a torus bundle over $\widetilde\Ecal$, with strata determined by the combinatorics of the fan.

Returning to the logarithmic setting, the first step is to define appropriate logarithmic structures on $\widetilde\Dcal$ and $\Ecal$. We equip $\widetilde\Dcal$ with the logarithmic structure obtained by first restricting the logarithmic structure on $\widetilde\VZ_{1,\alpha}(\PP^N|H,d)$ and then quotienting by the normal direction to $\widetilde\Dcal$. By the same process we may also define a logarithmic structure on $\Ecal$, and this coincides with the pull-back along the splitting morphism $\rho$ of the product logarithmic structure on the fibre product in \eqref{IIIa fibre product}. The map $\widetilde\Dcal \to \Ecal$ is then naturally a logarithmic map.

The next step is to construct $\widetilde\Ecal$ as a logarithmic modification of $\Ecal$, and to do this we need to describe the tropicalisation of the map $\widetilde\Dcal \to \Ecal$. In fact, it is more convenient to consider the \emph{extended tropicalisation} \cite{}. We begin by fixing notation. Associated to the combinatorial type $\Delta$, we have stable vertices $\sqC_0,\sqC_1,\ldots,\sqC_r$ with $\sqC_0$ corresponding to the core and $\sqC_1,\ldots,\sqC_r$ corresponding to stable vertices which lie on the raidus (see Lemma \ref{} above). For $i \in \{1,\ldots,r\}$ let $e_i$ denote the sum of the edge lengths separating $\sqC_i$ from $\sqC_0$. These give functions on the cone $\sigma$, and $\tau$ is the ray inside $\sigma$ given by the equations $e_1=\cdots=e_r$. Note that the $e_i$ also define functions on any cone belonging to the star of $\sigma$.

@@

Consider therefore any cone $\rho$ belonging to the star of $\tau$. Since the tropicalisation of $\widetilde\VZ_{1,\alpha}(\PP^N|H,d)$ is a subdivision of the tropicalisation of $\ol\Mcal_{1,\alpha}(\PP^N|H,d)$ there is a unique minimal cone in the star of $\sigma$ which contains $\rho$. We denote this cone by $\theta$, and remark that $\theta$ arises from a choice of combinatorial type which specialises the combinatorial type $\Delta$ defining $\sigma$. This means that each vertex $\sqC_i$ of the combinatorial type $\Delta$ may degenerate into a subgraph of the combinatorial type on $\theta$. Thus, on $\theta$ we have the edge length functions $e_1,\ldots,e_r$ as well as additional edge length functions corresponding to nodes on $\theta$ which are smoothed out on $\sigma$.

Now, $\rho$ is defined inside $\theta$ by a number of equalities and inequalities involving these edge lengths. These (in)equalities relate the distances to the core of various vertices of the dual graph. There are three cases which we must consider:
\begin{enumerate}
\item both vertices are components of the subgraph $\sqC_1 \cup \ldots \cup \sqC_r$;
\item both vertices are components of the subgraph $\sqC_0$;
\item one vertex is a component of $\sqC_0$ and one is a component of $\sqC_1 \cup \ldots \cup\sqC_r$.
\end{enumerate}
We start with Case (1). By the definition of the subdivision, we see that all take the form
\begin{equation*} f_i + e_i \st f_j + e_j, \qquad \st \in \{ =, < \} \end{equation*}
where $f_i$ and $f_j$ are positive linear combinations of additional edge length parameters which are set to zero in $\tau$. We may now pass to the subcone of $\rho$ obtained by imposing the additional equations $e_1=\ldots=e_r$. Note that this is \emph{not} a subcone of $\tau$ in general, since there are additional edge lengths which must be set to zero if one wishes to recover $\tau$. The additional equations mean that we can rewrite our previous (in)equalities in the form
\begin{equation*} f_i \st f_j, \qquad \st \in \{=,<\}\end{equation*}
and these define a cone in the limiting locus $e_1=\ldots=e_r=\infty$. By definition this is one of the cones in the subdivision of the extended tropicalisation of $\Ecal$, and all such cones are obtained in this manner.

Taking this subdivision amounts to the following modular blow-up of the fibre product of the moduli spaces attached to the vertices $\sqC_1,\ldots,\sqC_r$: given a logarithmic map with splitting nodes $q_1,\ldots,q_r$ as specified by the shape of $\Delta$, we glue together the $r$ vertices of the tropicalisation which carry the splitting nodes, and declare the resulting special vertex to be the root of the resulting tree. We then impose a central alignment condition, entirely analogous to the genus one construction, where the special root takes on the r\^ole previously occupied by the core.

We now address Case (2). These (in)equalities are not affected at all in the limit $e_1=\ldots=e_r=\infty$ and so the effect is to replace the factor of $\Ecal$ attached to the vertex $\sqC_0$
\begin{equation*} \ol\Mcal^{\leftrightarrow}_{\Gamma_{\tiny{\sqC_0}}}(P|H_0+H_\infty) \end{equation*}
with the radially aligned rubber space:
\begin{equation*} \VZ^{\leftrightarrow}_{\Gamma_{\tiny{\sqC_0}}}(P|H_0+H_\infty).\end{equation*}
The factorisation condition here is accounting for the ``fibre-direction'' factorisation. The ``base-direction'' factorisation plays no role here, since $\sqC_0$ is assigned zero horizontal degree (the base direction factorisation will enter the picture when we come to describe $\Dcal$).

It remains to discuss Case (3). Here we have a relation of the form $f_i = f_j + e_j$, so when we set $e_j =\infty$ there is no limiting cone. Therefore these relations to not appear in the modification of $\Ecal$.

To summarise: the subdivision induces a logarithmic modification $\widetilde\Ecal \to \Ecal$ which admits a modular description as a fibre product of genus zero centrally aligned maps (coming from the vertices $\sqC_1,\ldots,\sqC_r$) and genus one radially aligned rubber maps satisfying fibre-direction factorisation (coming from the vertex $\sqC_0$).

By construction, we have a map $\widetilde\Dcal \to \widetilde\Ecal$ which is a compactification of a torus bundle over $\widetilde\Ecal$. The strata of $\widetilde\Dcal$ can be read off from its tropicalisation, and in particular we have the information of how (polynomials in) the classes of boundary strata push forward to $\widetilde\Ecal$.

@@

\subsubsection{$\Dcal$ from $\widetilde\Dcal$}\label{subsection D from Dtilde} On $\widetilde\Dcal$ there is a natural vector bundle arising from the modular desription of $\widetilde\VZ_{1,\alpha}(\PP^N|H,d)$, namely:
\begin{equation*} F = \OO(\delta)^{\oplus r}. \end{equation*}
We claim that the fibre of $F$ over a moduli point can be naturally identified with
\begin{equation*} \left( \bigoplus_{i=1}^r \TT_{p_i} C_i^\prime \right) \otimes \TT_{C_0} \end{equation*}
where $C_i^\prime$ is a component of $C_i$ which lies on the radius, $p_i$ is the adjacent node which points towards the core, and $\TT_{C_0}$ is the universal tangent line bundle on the radially aligned rubber space.
